---
title: Predicting Chocolate Ratings Using Text Predictors
---
  
  
```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
theme_set(theme_minimal())

```



```{r Load-data}
url <- "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-18/chocolate.csv"
chocolate <- read_csv(url)

chocolate %>%
  ggplot(aes(rating)) +
  geom_histogram(bins = 15)
```


We will use text as predictors, thus we will have to perform text preprocessing


```{r text-summary}
library(tidytext)

tidy_chocolate <-
  chocolate %>%
  unnest_tokens(word, most_memorable_characteristics)

tidy_chocolate %>%
  count(word, sort = TRUE)
```


Data Exploration for the text

```{r}
tidy_chocolate %>%
  group_by(word) %>%
  summarise(
    n = n(),
    rating = mean(rating)
  ) %>%
  ggplot(aes(n, rating)) +
  geom_hline(
    yintercept = mean(chocolate$rating), lty = 2,
    color = "gray50", size = 1.5
  ) +
  geom_jitter(color = "midnightblue", alpha = 0.7) +
  geom_text(aes(label = word),
    check_overlap = TRUE, family = "IBMPlexSans",
    vjust = "top", hjust = "left"
  ) +
  scale_x_log10()
```


Model

```{r data-budget}
library(tidymodels)

set.seed(123)
choco_split <- initial_split(chocolate, strata = rating)
choco_train <- training(choco_split)
choco_test <- testing(choco_split)

set.seed(234)
choco_folds <- vfold_cv(choco_train, strata = rating)
choco_folds
```


Preprocess text data


```{r text-preprocessing}
library(textrecipes)

choco_rec <-
  recipe(rating ~ most_memorable_characteristics, data = choco_train) %>%
  step_tokenize(most_memorable_characteristics) %>%
  
  ## we retain only tokens with freq >= 100
  step_tokenfilter(most_memorable_characteristics, max_tokens = 100) %>%
  
  ## get the tf-idf
  step_tfidf(most_memorable_characteristics)

## just to check this works
prep(choco_rec) %>% bake(new_data = NULL)
```

Random Forest

```{r random-forest}
rf_spec <-
  rand_forest(trees = 500) %>%
  set_mode("regression")

rf_spec
```

SVM

```{r svm}
svm_spec <-
  svm_linear() %>%
  set_mode("regression")

svm_spec
```



```{r model-workflows}
svm_wf <- workflow(choco_rec, svm_spec)
rf_wf <- workflow(choco_rec, rf_spec)
```


Model Evaluation - with resamples
We are tuning nothing 

```{r resampling-for-parameter-tuning}
doParallel::registerDoParallel()

## save the predictions from the resamples training
contrl_preds <- control_resamples(save_pred = TRUE)

svm_rs <- fit_resamples(
  svm_wf,
  resamples = choco_folds,
  control = contrl_preds
)

ranger_rs <- fit_resamples(
  rf_wf,
  resamples = choco_folds,
  control = contrl_preds
)
```


Model Performance

```{r svm-performance}
collect_metrics(svm_rs)
```

The SVM performance here is somehow not very appealing


```{r random-forest-performance}
collect_metrics(ranger_rs)
```

The random forest performance here is somehow not very appealing and slightly worse than that of SVM

Visualize the results - for each of the folds


```{r}
bind_rows(
  collect_predictions(svm_rs) %>%
    mutate(mod = "SVM"),
  collect_predictions(ranger_rs) %>%
    mutate(mod = "ranger")
) %>%
  ggplot(aes(rating, .pred, color = id)) +
  geom_abline(lty = 2, color = "gray50", size = 1.2) +
  geom_jitter(width = 0.5, alpha = 0.5) +
  facet_wrap(vars(mod)) +
  coord_fixed()
```

We choose SVM to train the data - it is faster to train. and has slightly higher performance. It also had slightly better performance than random forest

```{r}
final_fitted <- last_fit(svm_wf, choco_split)
collect_metrics(final_fitted) ## metrics evaluated on the *testing* data
```

Extract the workflow - the object contains a fitted workflow that we can use for prediction

```{r svm-final-workflow}
final_wf <- extract_workflow(final_fitted)
predict(final_wf, choco_test)
```


```{r visualize-the-final-model}
extract_workflow(final_fitted) %>%
  tidy() %>%
  filter(term != "Bias") %>%
  group_by(estimate > 0) %>%
  slice_max(abs(estimate), n = 10) %>%
  ungroup() %>%
  mutate(term = str_remove(term, "tfidf_most_memorable_characteristics_")) %>%
  ggplot(aes(estimate, fct_reorder(term, estimate), fill = estimate > 0)) +
  geom_col(alpha = 0.8) +
  scale_fill_discrete(labels = c("low ratings", "high ratings")) +
  labs(y = NULL, fill = "More from...")
```


